---
title: "통계 학습 개론 2주차"
output: html_notebook
---

## Linear Regression
 * MASS(Modern Applied Stattistics with S)
   * https://cran.r-project.org/web/packages/MASS/MASS.pdf
 * ISRL (an Introduction to Statistical Learning in R)
   * https://cran.r-project.org/web/packages/ISLR/ISLR.pdf
```{r}
library(MASS)
library(ISLR)
```

## Boston
 * The Boston data frame has 506 rows and 14 columns. (on MASS)
 
### The format
 * This data frame contains the following columns:
   * `crim` per capita crime rate by town.
   * `zn` proportion of residential land zoned for lats over 25,000 sq.ft
   * `indus` proportion of non-retail business acres per town.
   * `chas` Charles River dummy variable (= 1 if tract bounds river; 0 other wise).
   * `nox` nitron oxiedes concentration (parts per 10 million).
   * `rm` average number of rooms per dwelling.
   * `age` proprtion of owner-occupied units built prior to 1940.
   * `dis` weighted mean of distances to five Boston employment centres.
   * `rad` index of accessibility to radial highways.
   * `tax` full-value property-tax rate per \$10.000
   * `ptratio` pupil-teacher ratio by twon.
   * `black` 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.
   * `lstat` lower status of the population (percent).
   * `medv` meadian value of owner-occupied homes in \$1000s.

### Target
 * We want to predict `medv` values from others variables.
   
```{r}
head(Boston)
```

 * First models to predict medv using lstat (medv = beta_0 + beta_1 * lstat)
```{r}
lm.fit <- lm(medv~lstat, data=Boston)
```

```{r}
summary(lm.fit)
```

 * Adj R squared = 0.5432
 * p-value = 2.2e-16
 * It means:
   * medv = beta_0 + beta_1 * lstat model is better than medv = beta_0 model.
   * but there are many other unexplained predictors.

```{r}
coefficients(lm.fit)
```

 * The coefficients of model is the value written above.
   * medv = 34.55 - 0.95 * lstat
   

```{r}
confint(lm.fit)
```

 * confidence interval of coefficients.
 
```{r}
predict(lm.fit, data.frame(lstat=c(5, 10, 15)), interval='confidence')
```
 * how to predict medv.

```{r}
summary(lm.fit)
```


```{r}
attach(Boston)
```
 * easy way to use variables from Boston using `attach`.


```{r}
plot(lstat, medv)
abline(lm.fit, col=2)
```
 * visualization
 
```{r}
plot(predict(lm.fit), rstudent(lm.fit))
abline(h=0)
```
```{r}
plot(hatvalues(lm.fit))
identify(hatvalues(lm.fit))
```

```{r}
lm.fit <- lm(medv~lstat + age, data=Boston)
summary(lm.fit)
```

```{r}
lm.fit <- lm(medv~., data=Boston)
summary(lm.fit)
```

```{r}
summary(lm.fit)$sigma
```

### Car
 * car(Companion to Applied Regression)
   * https://cran.r-project.org/web/packages/car/car.pdf
```{r}
library(car)
```


```{r}
vif(lm.fit)
```
 * VIF(Variance Inflation Factor)
   * The larger VIF, the greater possibility of multicollinearity.
   * Rule of thumb : VIF > 5 or VIF > 10 => multicollinearity.


```{r}
lm.fit1 = update(lm.fit, ~.-age)
summary(lm.fit1)
```

```{r}
summary(lm(medv~lstat*age))
```

```{r}
lm.fit2 = lm(medv~lstat + I(lstat^2))
```


```{r}
anova(lm.fit, lm.fit2)
```


```{r}
lm.fit5 = lm(medv~poly(lstat, 5))
summary(lm.fit5)
```

* Quantative
```{r}
lm.fit = lm(Sales~.+Income: Advertising + Price:Age, data=Carseats)
summary(lm.fit)
```

```{r}
contrasts(Carseats$ShelveLoc)
```




